On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-03-25 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Bibliography: use []s instead of dots
[J220] Capitalization issues

\makeatletter
\renewcommand{\@biblabel}[1]{#1.} % Заменяем библиографию с квадратных скобок на точку:
\makeatother %Смысл этих трёх строчек мне непонятен, но поверим "Запискам дебианщика"

@@

Sections 2--4 are devoted to the linear lower bound.
Each Section consists of 2 Subsections: General results and Special results.
In General results, we do not aim to provide tight estimates;
they are discussed in Special results.

@@

Let us introduce the Problem, basic notions and results.

>>>>

@@

Sections 2--4 are devoted to the linear lower bound.
Each section consists of 2 subsections: General results and Special results.
In General results, we do not aim to provide tight estimates;
they are discussed in Special results.

@@

Let us introduce the problem, basic notions and results.
